---
title: "Untitled"
author: "Jonathan Leong"
date: "8/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import Libraries

```{r}
library(ggplot2)
library(dplyr)
library(readr)
library(tidyr)
library(rjson)
library(jsonlite)
library(RCurl)
library(MASS)
```

## Extract HDB Resale Data using API query

#extract entries from 2017-2019
```{r, echo=FALSE}

url <- "https://data.gov.sg/api/action/datastore_search?resource_id=42ff9cfe-abe5-4b54-beda-c88f9bb438ee&limit=150000"
fullurl <- URLencode(url)


#import data from website to dataframe
data1 <- fromJSON(getURL(fullurl))

HDB_data_1719 <- data1$result$records

head(HDB_data_1719)

```

#extract entries from 2015-2016
```{r}

url <- "https://data.gov.sg/api/action/datastore_search?resource_id=1b702208-44bf-4829-b620-4615ee19b57c&limit=38000"
fullurl <- URLencode(url)


#import data from website to dataframe
data2 <- fromJSON(getURL(fullurl))

HDB_data_1516 <- data2$result$records

```

#extract entries from 2012-2014
```{r}

url <- "https://data.gov.sg/api/action/datastore_search?resource_id=83b2fc37-ce8c-4df4-968b-370fd818138b&limit=55000"
fullurl <- URLencode(url)


#import data from website to dataframe
data3 <- fromJSON(getURL(fullurl))

HDB_data_1214 <- data3$result$records

```

#extract entries from 2000-2012
```{r}

url <- "https://data.gov.sg/api/action/datastore_search?resource_id=8c00bf08-9124-479e-aeca-7cc411d884c4&limit=370000"
fullurl <- URLencode(url)


#import data from website to dataframe
data4 <- fromJSON(getURL(fullurl))

HDB_data_0012 <- data4$result$records

```

```{r}
HDB_data <- rbind(HDB_data_0012,HDB_data_1214)
HDB_data_1516_2 <- HDB_data_1516[, -8]
HDB_data <- rbind(HDB_data, HDB_data_1516_2)
HDB_data_1719_2 <- HDB_data_1719[, -8]
HDB_data <- rbind(HDB_data, HDB_data_1719_2)
```

# Export Intermediate File
```{r}
write_csv(HDB_data, path = "HDB Resale data.csv")
```

#Download Longitude/Latitude and X/Y Coordinates from Onemap
```{r}
all_addresses <- paste(HDB_data$block, HDB_data$street_name)

HDB_data$full_address <- all_addresses

unique_addresses <- unique(all_addresses)
```

```{r}
latitude_list <- c()
longitude_list <- c()
X_list <- c()
Y_list <- c()
options(digits = 20)

for (i in c(1:3000)) {
  addurl <- paste0("https://developers.onemap.sg/commonapi/search?searchVal=",
                   unique_addresses[i],
                   "&returnGeom=Y&getAddrDetails=N&pageNum=1")
  
  address_search <- URLencode(addurl)
  search_result <- fromJSON(address_search)
  
  if (as.numeric(search_result$found) > 0) {
    latitude <- as.numeric(search_result$results[1,]['LATITUDE'])
    longitude <- as.numeric(search_result$results[1,]['LONGITUDE'])
    X <- as.numeric(search_result$results[1,]['X'])
    Y <- as.numeric(search_result$results[1,]['Y'])
  } else {
    latitude <- 0
    longitude <- 0
    X <- 0
    Y <- 0
  }
  
  latitude_list <- append(latitude_list, latitude)
  longitude_list <- append(longitude_list, longitude)
  X_list <- append(X_list, X)
  Y_list <- append(Y_list, Y)
  
}
```

```{r}
latitude_list2 <- c()
longitude_list2 <- c()
X_list2 <- c()
Y_list2 <- c()

for (i in c(3001:6000)) {
  addurl <- paste0("https://developers.onemap.sg/commonapi/search?searchVal=",
                   unique_addresses[i],
                   "&returnGeom=Y&getAddrDetails=N&pageNum=1")
  
  address_search <- URLencode(addurl)
  search_result <- fromJSON(address_search)
  
  if (as.numeric(search_result$found) > 0) {
    latitude <- as.numeric(search_result$results[1,]['LATITUDE'])
    longitude <- as.numeric(search_result$results[1,]['LONGITUDE'])
    X <- as.numeric(search_result$results[1,]['X'])
    Y <- as.numeric(search_result$results[1,]['Y'])
  } else {
    latitude <- 0
    longitude <- 0
    X <- 0
    Y <- 0
  }
  
  latitude_list2 <- append(latitude_list2, latitude)
  longitude_list2 <- append(longitude_list2, longitude)
  X_list2 <- append(X_list2, X)
  Y_list2 <- append(Y_list2, Y)
  
}
```

```{r}
latitude_list3 <- c()
longitude_list3 <- c()
X_list3 <- c()
Y_list3 <- c()

for (i in c(6001:9165)) {
  addurl <- paste0("https://developers.onemap.sg/commonapi/search?searchVal=",
                   unique_addresses[i],
                   "&returnGeom=Y&getAddrDetails=N&pageNum=1")
  
  address_search <- URLencode(addurl)
  search_result <- fromJSON(address_search)
  
  if (as.numeric(search_result$found) > 0) {
    latitude <- as.numeric(search_result$results[1,]['LATITUDE'])
    longitude <- as.numeric(search_result$results[1,]['LONGITUDE'])
    X <- as.numeric(search_result$results[1,]['X'])
    Y <- as.numeric(search_result$results[1,]['Y'])
  } else {
    latitude <- 0
    longitude <- 0
    X <- 0
    Y <- 0
  }
  
  latitude_list3 <- append(latitude_list3, latitude)
  longitude_list3 <- append(longitude_list3, longitude)
  X_list3 <- append(X_list3, X)
  Y_list3 <- append(Y_list3, Y)
  
}
```

```{r}
latitude_list_full <- append(latitude_list, latitude_list2)
latitude_list_full <- append(latitude_list_full, latitude_list3)

longitude_list_full <- append(longitude_list, longitude_list2)
longitude_list_full <- append(longitude_list_full, longitude_list3)

X_list_full <- append(X_list, X_list2)
X_list_full <- append(X_list_full, X_list3
                 )
Y_list_full <- append(Y_list, Y_list2)
Y_list_full <- append(Y_list_full, Y_list3)
```

```{r}
unique_addresses2 <- data.frame(unique_addresses,latitude_list_full, longitude_list_full, X_list_full, Y_list_full)

HDB_data_with_Location <- merge(HDB_data, unique_addresses2, by.x = "full_address", by.y = "unique_addresses")
```

```{r}
write_csv(unique_addresses2, path = "Unique HDB Address.csv")

write_csv(HDB_data_with_Location, path = "HDB Resale data with Location.csv")
```

## Get MRT Location Data
```{r}
MRT <- read_csv("MRT list.csv")
```

```{r}
latitude_list <- c()
longitude_list <- c()
X_list <- c()
Y_list <- c()

for (i in c(1:119)) {
  addurl <- paste0("https://developers.onemap.sg/commonapi/search?searchVal=",
                   MRT$Address[i],
                   "&returnGeom=Y&getAddrDetails=N&pageNum=1")
  
  address_search <- URLencode(addurl)
  search_result <- fromJSON(address_search)
  
  if (as.numeric(search_result$found) > 0) {
    latitude <- as.numeric(search_result$results[1,]['LATITUDE'])
    longitude <- as.numeric(search_result$results[1,]['LONGITUDE'])
    X <- as.numeric(search_result$results[1,]['X'])
    Y <- as.numeric(search_result$results[1,]['Y'])
  } else {
    latitude <- 0
    longitude <- 0
    X <- 0
    Y <- 0
  }
  
  latitude_list <- append(latitude_list, latitude)
  longitude_list <- append(longitude_list, longitude)
  X_list <- append(X_list, X)
  Y_list <- append(Y_list, Y)
  
}
```

```{r}
MRT_with_locations <- data.frame(MRT$MRT_station, MRT$Address, latitude_list, longitude_list, X_list, Y_list)
write_csv(MRT_with_locations, path = "MRT with Location.csv")
```

## Identify Closest MRT for each Resale and Calculate Distance
```{r}
closest_MRT <- c()
closest_distance <- c()

for (i in c(1:9165)) {
  distance <- 999999999999999999999999999
  
  for (j in c(1:119)) {
    
    euclidean <- sqrt((unique_addresses2$X_list[i]-MRT_with_locations$X_list[j])^2 + 
                        (unique_addresses2$Y_list[i]-MRT_with_locations$Y_list[j])^2)
    
    if (euclidean < distance) {
      
      distance <- euclidean
      closest <- MRT_with_locations$MRT.MRT_station[j]
      
    }
    
  }
  
  closest_MRT <- append(closest_MRT, closest)
  closest_distance <- append(closest_distance, distance)
  
}
```

```{r}
unique_addresses_with_MRT <- data.frame(unique_addresses2, closest_MRT, closest_distance)
unique_addresses_with_MRT$latitude_list_full <- NULL
unique_addresses_with_MRT$longitude_list_full <- NULL
unique_addresses_with_MRT$X_list_full <- NULL
unique_addresses_with_MRT$Y_list_full <- NULL

HDB_data_final <- merge(HDB_data_with_Location, unique_addresses_with_MRT, by.x = "full_address", by.y = "unique_addresses")
```

## Calculate Distance of each REsale to CBD
```{r}
RP <- "Raffles Place"
CBD_RP <- subset(MRT_with_locations, MRT.MRT_station %in% RP)

HDB_data_final$CBD_dist <- sqrt((HDB_data_final$X_list_full - CBD_RP$X_list)^2 + (HDB_data_final$Y_list_full - CBD_RP$Y_list)^2)
```

```{r}
write_csv(HDB_data_final, path = "HDB Resale data final.csv")
```

## Calculate Mean Price amd Mean Price per SQM
```{r}
HDB_data_final$floor_area_sqm <- as.numeric(as.character(HDB_data_final$floor_area_sqm))
HDB_data_final$resale_price <- as.numeric(as.character(HDB_data_final$resale_price))
HDB_data_final$price_per_sqm <- HDB_data_final$resale_price/HDB_data_final$floor_area_sqm

year_month <- setNames(data.frame(HDB_data_final$month,
                                  do.call(rbind, strsplit(as.character(HDB_data_final$month),
                                                          split="-"))),
                       c("attr", "year", "month"))
year_month$attr <- NULL
year_month$month <- NULL
```

#calculate mean price
```{r}
HDB_with_year <- data.frame(HDB_data_final, year_month)
HDB_with_year$year <- as.numeric(as.character(HDB_with_year$year))

year_and_price <- data.frame(HDB_with_year$resale_price, HDB_with_year$year)
mean_yearly_price <- aggregate(.~HDB_with_year.year, data = year_and_price, mean)

write_csv(mean_yearly_price, path = "Mean Price HDB.csv")
```

#calculate mean price per sqm
```{r}
year_and_price_sqm <- data.frame(HDB_with_year$price_per_sqm, HDB_with_year$year)
mean_yearly_price_sqm <- aggregate(.~HDB_with_year.year, data = year_and_price_sqm, mean)

write_csv(mean_yearly_price_sqm, path = "Mean Price per sqm HDB.csv")
```


## Multiple Linear Regression Calculation
```{r}
fit <- lm(resale_price ~ flat_type + flat_model + floor_area_sqm + storey_range + closest_distance + CBD_dist + lease_commence_date,
          data = HDB_data_final)

summary(fit)
```

```{r}
fit2 <- lm(resale_price ~ flat_type + flat_model + floor_area_sqm + storey_range + CBD_dist,
           data = HDB_data_final)

summary(fit2)
```

##Stepwise model selection
```{r}
fit3 <- lm(resale_price ~ flat_type + flat_model + floor_area_sqm + storey_range + closest_distance + CBD_dist + lease_commence_date,
           data = HDB_data_final)
step <- stepAIC(fit3, direction = "both")
step$anova
```

